Simply Grasping Simple Shapes:\\ Commanding a Humanoid Hand with a Shape-Based Synergy

### 2017-10-31 draft_springer_2.tex
edited for spelling and grammar

The first step was to build an initial model for grasping by determining the finger angles for grasps of cylinders of specific diameters that span the size range of objects that might be encountered in the workspace. For this application, the chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm. For the program, the objects were considered massless. The internal contact model in SynGrasp was used to design the grip. This model performed better than traditional inverse kinematic models because it allowed contact with multiple points on the hand rather than only a single point-of-interest on the end-effector. The key features of the R2 hand such as the number of  DoF, finger length, joint rotation frames, and actuation scheme were matched. The SyGrasp toolbox did not allow for representation of the R2 hands physical compliance, nor could the geometry of the palm be accurately represented.

@@

\subsection{Model Refinement and Synergy Development} 
A simple testing method was used to validate the initial SynGrasp models. A cylindrical object was placed on the table, touching R2's open palm. All fingers were fully extended in the starting position. The object's placement along the palm was varied from near the base of the fingers to the base of the thumb, approximately 5cm. This allowed testing of uncertainty in position that will be present when the object must be localized. Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table. Successful completion of this set of motions demonstrates a firm grasp on the object through a large motion of the robot as shown in Fig \ref{testing}.

@@

\subsection{Testing Protocol}
After adjusting the grasp models and generating the joint angle fits to data for the four cylindrical validation objects, fifteen objects typically manipulated using a cylindrical grasp were grasped using the R2 hand and the SynGrasp geometrical synergy grasping model. These objects ranged from 2.79 to 8.4 cm in diameter and 5 g to 1.02 kg in mass. In addition, five non-cylindrical objects were manipulated using the same action illustrated in Fig \ref{thumb_fits}. These objects included four shapes resembling rectangular prisms and one hand drill. For a grasp to be considered successful, the object needed to be grasped by R2, lifted from a table top and held without slipping as it was rotated by the robot as shown in Fig. \ref{testing}.

>>>>

The first step was to build an initial model for grasping by determining the finger angles for grasps of cylinders of specific diameters that span the size range of objects that might be encountered in the workspace. For this application, the chosen diameters for grasped objects were 2.54 cm, 3.81 cm, 5.08 cm, and 7.62 cm. For the program, the objects were considered massless. The internal contact model in SynGrasp was used to design the grip. This model performed better than traditional inverse kinematic models because it allowed contact with multiple points on the hand rather than only a single point-of-interest on the end-effector. The key features of the R2 hand such as the number of  DoF, finger length, joint rotation frames, and actuation scheme were matched. The SynGrasp toolbox did not allow for representation of the R2 hands physical compliance, nor could the geometry of the palm be accurately represented.

@@

\subsection{Model Refinement and Synergy Development} 
A simple testing method was used to validate the initial SynGrasp models. A cylindrical object was placed on the table, touching R2's open palm. All fingers were fully extended in the starting position. The object's placement along the palm was varied from near the base of the fingers to the base of the thumb, approximately 5 cm. This allowed testing of uncertainty in position that will be present when the object must be localized. Then, the robot was commanded to close its hand based on the synergy values, lift the object, rotate the object upside down, return it to straight, and finally, release it back on the table. Successful completion of this set of motions demonstrates a firm grasp on the object through a large motion of the robot as shown in Fig \ref{testing}.

@@

\subsection{Testing Protocol}
After adjusting the grasp models and generating the joint angle fits to data for the four cylindrical validation objects, fifteen objects typically manipulated using a cylindrical grasp were grasped using the R2 hand and the SynGrasp geometrical synergy grasping model. These objects ranged from 2.79 to 8.4 cm in diameter and 5 g to 1.02 kg in mass. In addition, five non-cylindrical objects were manipulated using the same action illustrated in Fig \ref{testing}. These objects included four shapes resembling rectangular prisms and one hand drill. For a grasp to be considered successful, the object needed to be grasped by R2, lifted from a table top and held without slipping as it was rotated by the robot as shown in Fig. \ref{testing}.
